---
title: "Standard Normal Distribution (Z) Table"
description: "The generated z-table, available for HTML and PDF formats"
format:
  html:
    toc: true
    toc-location: left
    theme: cosmo
    css: styles.css
    embed-resources: false
  pdf:
    output-file: z-table.pdf
    documentclass: article
    geometry: 
      - margin=0.5in
      - paperheight=11in
      - paperwidth=8.5in
    fontsize: 9pt
    keep-tex: false
    include-in-header:
      text: |
        \usepackage{caption}
        \captionsetup[table]{skip=2pt}
        \setlength{\abovecaptionskip}{2pt}
        \setlength{\belowcaptionskip}{2pt}
execute:
  echo: false
  warning: false
  message: false
engine: knitr
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
box::use(./z_table[create_z_table])
```

::: {.content-visible when-format="html"}
## Download PDF Version

{{< downloadthis z-table.pdf dname="z-table" label="Download Z-Table (PDF)" icon="file-earmark-pdf" type="info" >}}
:::

::: {.content-visible when-format="pdf"}
\vspace{-10pt}
:::

## About the Z-Table

This table shows the cumulative probability (area under the curve) to the *left* of a given z-score in a standard normal distribution.

- **Rows**: z-score to first decimal place | **Columns**: second decimal place | **Values**: Cumulative probability $P(Z \leq z)$

::: {.content-visible when-format="pdf"}
\vspace{-5pt}
:::

## Positive Z-Scores

```{r positive-z-table}
create_z_table(
    z_range = c(0, 4),
    caption = "Standard Normal Distribution - Positive Z-Scores",
    header_color = "#4a90e2"
)
```

::: {.content-visible when-format="pdf"}
\vspace{-8pt}
:::

## Negative Z-Scores

```{r negative-z-table}
create_z_table(
    z_range = c(-4, 0),
    caption = "Standard Normal Distribution - Negative Z-Scores",
    header_color = "#e24a4a"
)
```

::: {.content-visible when-format="pdf"}
\vspace{-5pt}
:::

## How to Use This Table

**Example:** For $z = 1.96$, find row "1.9" and column ".06". The value 0.9750 means 97.50% of values fall below $z = 1.96$.
